si: code and prose exploring Spatial Interaction models

### 2022-04-15 README.qmd
Actions badge
Former-commit-id: a6fe4071ab57225a8e27a5445dbb5d0f79cec1fe
Update README with more resources

<!-- badges: start -->

<!-- badges: end -->

@@

TBC.

@@

-   Reproducible code implementing SIMs in R (based on the outdated `sp` class system): https://rpubs.com/adam_dennett/257231

-

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/robinlovelace/si/workflows/R-CMD-check/badge.svg)](https://github.com/robinlovelace/si/actions)
<!-- badges: end -->

@@

@@

- Reproducible [code](https://rpubs.com/adam_dennett/257231) implementing SIMs in R by Adam Dennet, based on the outdated `sp` class system, and based on [`sf` classes](https://github.com/adamdennett/LondonSchoolsSIM/blob/main/Schools.Rmd)

- The [`spflow` R package](https://github.com/LukeCe/spflow) on CRAN

- The [`spint` Python package](https://spint.readthedocs.io/en/latest/)
